% ── Referências ─────────────────────────────────────────────────────────────
\capitulopostext{REFERÊNCIAS}

\begin{singlespace}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

CODD, E. F. A Relational Model of Data for Large Shared Data Banks. \textbf{Communications of the ACM}, v. 13, n. 6, p. 377-387, 1970.

\vspace{\baselineskip}

DIJKSTRA, E. W. The Humble Programmer. \textbf{Communications of the ACM}, v. 15, n. 10, p. 859-866, 1972.

\vspace{\baselineskip}

DJANGO SOFTWARE FOUNDATION. \textbf{Django documentation.} Version 5.2. 2025. Disponível em: \url{https://docs.djangoproject.com/en/5.2/}. Acesso em: mar. 2026.

\vspace{\baselineskip}

DOCKER INC. \textbf{Docker Documentation.} 2024. Disponível em: \url{https://docs.docker.com/}. Acesso em: mar. 2026.

\vspace{\baselineskip}

ELMASRI, R.; NAVATHE, S. B. \textbf{Sistemas de banco de dados.} 6. ed. São Paulo: Pearson Addison Wesley, 2011.

\vspace{\baselineskip}

FIELDING, R. T. \textbf{Architectural Styles and the Design of Network-based Software Architectures.} 2000. Tese (Doutorado em Ciência da Computação) -- University of California, Irvine, 2000.

\vspace{\baselineskip}

HUMBLE, J.; FARLEY, D. \textbf{Continuous Delivery:} Reliable Software Releases through Build, Test, and Deployment Automation. Upper Saddle River: Addison-Wesley, 2010.

\vspace{\baselineskip}

LÜCK, H. \textbf{Dimensões da gestão escolar e suas competências.} Curitiba: Positivo, 2009.

\vspace{\baselineskip}

MARTIN, R. C. \textbf{Clean Code:} A Handbook of Agile Software Craftsmanship. Upper Saddle River: Prentice Hall, 2009.

\vspace{\baselineskip}

MELL, P.; GRANCE, T. \textbf{The NIST Definition of Cloud Computing.} Gaithersburg: National Institute of Standards and Technology, 2011. (Special Publication 800-145).

\vspace{\baselineskip}

MORAN, J. M. Mudando a educação com metodologias ativas. In: SOUZA, C. A. de; MORALES, O. E. T. (Org.). \textbf{Convergências midiáticas, educação e cidadania:} aproximações jovens. Ponta Grossa: UEPG, 2015. p. 15-33.

\vspace{\baselineskip}

PRESSMAN, R. S.; MAXIM, B. R. \textbf{Engenharia de Software:} uma abordagem profissional. 8. ed. Porto Alegre: AMGH, 2016.

\vspace{\baselineskip}

SOMMERVILLE, I. \textbf{Engenharia de Software.} 9. ed. São Paulo: Pearson Prentice Hall, 2011.

\vspace{\baselineskip}

W3C -- WORLD WIDE WEB CONSORTIUM. \textbf{Web Content Accessibility Guidelines (WCAG) 2.1.} 2018. Disponível em: \url{https://www.w3.org/TR/WCAG21/}. Acesso em: mar. 2026.

\end{singlespace}
